Perturbation theory in the complex plane: Exceptional points and where to find them

### 2020-11-16 Manuscript/EPAWTFT.tex
Added meshes and cylinders to figures, and sorted UMP axis labels

\author{Antoine \surname{Marie}}
\affiliation{\LCPQ}
\author{Hugh G.~A.~\surname{Burton}}
%\affiliation{\UCAM}
\affiliation{\UOX}
%\author{Paola \surname{Gori-Giorgi}}
%\affiliation{\VU}
\author{Pierre-Fran\c{c}ois \surname{Loos}}
\email{loos@irsamc.ups-tlse.fr}
\affiliation{\LCPQ}

@@

%%% FIG 3 %%%
\begin{figure*}
	\includegraphics[height=0.25\textwidth]{fig3a}	
	\hspace{0.05\textwidth}
	\includegraphics[height=0.25\textwidth]{fig3b}
	\hspace{0.05\textwidth}
	\includegraphics[height=0.25\textwidth]{fig3c}	
	\caption{
	Convergence of the URMP series as a function of the perturbation order $n$ energies for the Hubbard dimer at $U/t = 3$ and $7$.
	The Riemann surfaces of the FCI energies are also represented for these two values of $U/t$. 
	\label{fig:UMP}}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~863481)
HGAB gratefully acknowledges New College, Oxford for funding through the Astor Junior Research Fellowship.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\author{Antoine \surname{Marie}}
\affiliation{\LCPQ}
\author{Hugh G.~A.~\surname{Burton}}
%\affiliation{\UCAM}
\email{hugh.burton@chem.ox.ac.uk}
\affiliation{\UOX}
%\author{Paola \surname{Gori-Giorgi}}
%\affiliation{\VU}
\author{Pierre-Fran\c{c}ois \surname{Loos}}
\email{loos@irsamc.ups-tlse.fr}
\affiliation{\LCPQ}

@@

%%% FIG 3 %%%
\begin{figure*}
    \centering
	\includegraphics[height=0.23\textwidth]{fig3a}	
	\hspace{0.05\textwidth}
	\includegraphics[height=0.23\textwidth]{fig3b}
	\hspace{0.05\textwidth}
	\includegraphics[height=0.23\textwidth]{fig3c}	
	\caption{
	Convergence of the URMP series as a function of the perturbation order $n$ energies for the Hubbard dimer at $U/t = 3$ and $7$.
	The Riemann surfaces of the FCI energies are also represented for these two values of $U/t$. 
	\label{fig:UMP}}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~863481).
HGAB gratefully acknowledges New College, Oxford for funding through the Astor Junior Research Fellowship.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
